A New Dual Terminal Sliding Mode Control Design For Rigid Robotic Manipulator

### 2016-11-14 paper3_manuscript.tex
20161114

\begin{abstract}
This paper proposes a dual terminal SMC scheme for the rigid robotic manipulator. \textcolor{red}{As a signiﬁcant novelty, the presented design technique integates the individual SM surfaces to achieve the finite time convergence of overall system states by utilizing specially designed construct, and accordingly the convergence time for the entire system is easily obtained due to the integral design. The underactuated issue and input limitation are specially considered in this paper, i.e., the underactuated issue are solved by introducing the hierarchical methodology into the basic dual SMC scheme. Combining the adaptive technique with the proposed method eliminates the adverse effect caused by the input limitation in the rigious stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the rigid robotic manipulator. Simulation results validate the theoretical analyses about the proposed method.
\end{abstract}
\begin{keyword}
Finite time control; Robotic manipulator control; TSM; Input limitation; Stability analysis
\end{keyword}
\end{frontmatter}
\section{Introduction}
\textcolor{red}{Variable structure systems (VSS) are best known due to their insensitivity to parametric uncertainties~\cite{slotine1991applied}, and have been widely used in engineering applications, such as DC and DC converters~\cite{Tan2008General}, network control schemes~\cite{Hou2016}, aircrafts~\cite{Loza2015Sensor}, tethered satellite systems~\cite{Ma201667}, robotic manipulators~\cite{Beak2016A} and so on. As one important branch of the VSS, the sliding mode control (SMC) has become a popular solution to different kinds of control and signal process issues in recent years~\cite{zhao2015nonlinear,zhang2015attitude}. Meza-S{\'a}nchez et al. applied the second-order SMC scheme to a 3-DOF helicopter prototype based on the experimental test bed~\cite{meza2015output}. Zheng et al. implemented the SMC law to eliminate the bad effect of the input quantization in the coding and decoding process~\cite{zheng2016sliding}. Guzman et al. investigated the application of a SMC in a power factor rectifier with the constant switching frequency~\cite{guzman2016sliding}. Said et al. designed a robust adaptive sliding mode method to ensure the asymptotically stability of a boost converter~\cite{oucheriah2013pwm}. Roughly speaking, the SMC scheme is competent for normal scientific missions, due to its insensitivity to parameteric uncertainties and external disturbances, however, there still exist some obstacles, such as noncontinuous switching inputs in high frequency and convergence speed design schemes~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some practical engineering applications~\cite{fridman2011sliding}.}

@@

and one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:second-order system}), providing the finite time convergence by using MDTSM technique.

@@

Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension can be excluded by using conventional TSM scheme, which results in that the remained $n-1$-link manipulator can be controlled by the proposed MDTSM scheme.

@@

The singularity of the MDTSM scheme for the robotic manipulator can be removed by using the technique introduced in Theorem \ref{theorem:3}.

>>>>

\begin{abstract}
This paper proposes a dual terminal sliding mode scheme for tracking tasks of rigid robotic manipulators. \textcolor{red}{As a signiﬁcant novelty, the presented design technique integates the individual sliding mode surfaces to achieve the finite time convergence of tracking errors utilizing specially designed construct, and accordingly the convergence time is easily obtained due to the integral design. The underactuated issue and input limitation are specially considered in this paper, i.e., the underactuated issue is solved by introducing the hierarchical methodology into the basic dual sliding mode controller. Combining the adaptive technique with the proposed method eliminates the adverse effect caused by the input limitation in the rigious stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the tracking tasks of the rigid robotic manipulator. Simulation results validate the theoretical analyses about the proposed method.
\end{abstract}
\begin{keyword}
Finite time control; Robotic manipulator control; Terminal sliding mode control; Input limitation; Stability analysis
\end{keyword}
\end{frontmatter}
\section{Introduction}
\textcolor{red}{Variable structure systems (VSS) are best known due to their insensitivity to parametric uncertainties~\cite{slotine1991applied}, and have been widely used in engineering applications, such as DC and DC converters~\cite{Tan2008General}, network control schemes~\cite{Hou2016}, aircrafts~\cite{Loza2015Sensor}, tethered satellite systems~\cite{Ma201667}, robotic manipulators~\cite{Beak2016A} and so on. As one important branch of the VSS, the sliding mode control (SMC) has become a popular solution to different kinds of control and signal process issues in recent years~\cite{zhao2015nonlinear,zhang2015attitude}. Meza-S{\'a}nchez et al. applied the second-order SMC scheme to a 3-DOF helicopter prototype based on the experimental test bed~\cite{meza2015output}. Zheng et al. implemented the SMC law to eliminate the bad effect of the input quantization in the coding and decoding process~\cite{zheng2016sliding}. Guzman et al. investigated the application of a SMC in a power factor rectifier with the constant switching frequency~\cite{guzman2016sliding}. Said et al. designed a robust adaptive sliding mode method to ensure the asymptotically stability of a boost converter~\cite{oucheriah2013pwm}. Roughly speaking, the SMC scheme is competent for normal scientific missions, due to its insensitivity to parameteric uncertainties and external disturbances, however, there still exist some obstacles, such as noncontinuous switching inputs in high frequency and convergence speed design schemes~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some practical engineering applications~\cite{fridman2011sliding}.}

@@

and one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:second-order system}), providing the finite time convergence using MDTSM technique.

@@

Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension can be excluded using conventional TSM scheme, which results in that the remained $n-1$-link manipulator can be controlled by the proposed MDTSM scheme.

@@

The singularity of the MDTSM scheme for the robotic manipulator can be removed using the technique introduced in Theorem \ref{theorem:3}.
